Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

   \multirow{2}{*}{sRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} NON
   		 & WSTS (downward + upward) Thm~9 \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline

@@

   \multirow{2}{*}{ {\bf sRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} NON
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable   \\ \hline
   \multirow{2}{*}{ {\bf BsRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline
   \multirow{2}{*}{ {\bf ksRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline

>>>>

   \multirow{2}{*}{sRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} 
   		 & WSTS (downward + upward) Thm~9 \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline

@@

   \multirow{2}{*}{ {\bf sRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} 
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable   \\ \hline
   \multirow{2}{*}{ {\bf BsRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline
   \multirow{2}{*}{ {\bf ksRP } } 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline
